\setchapterstyle{kao}
\setchapterpreamble[u]{\margintoc}
\chapter{Ella's Amazing Brioche Buns for Burgers}

\section{Ingredients}

\begin{multicols}{2}
\begin{description}
	\item[200 ml] Water
	\item[1] egg + $1$ for egg-wash
	\item[\rev{4 Spoons}] Milk
	\item[\rev{1 Cube}] Fresh Yeast
	\item[35 g] Sugar
	\item[8 g] Salt
	\item[80 g] Cold butter
	\item[500 g] Strong flour
\end{description}
\end{multicols}	

\section{Preparation}
Separate the butter for later.

First, add all other ingredients in a bow and mix them until everything is combined. It does not need to be smooth, as long as you do not have large amounts of flower anywhere in the bow.
%
Then, wait $30$ minutes before start kneading the dough\sidenote{During this time the proteins in the flower will start combining with the help of the water (\href{https://www.kingarthurflour.com/blog/2017/09/29/using-the-autolyse-method}{autolyze}), forming gluten. If you start knead before this, you will be kneading while the gluten forms, which is a waste of time.
%
Relax and clean the space in the meanwhile.}.

When the dough is kneaded, start adding the butter in chunks.
%
Here, if you are doing this by hand, you can add a chunk, fold a bit the dough, and add another chunk, go folding until no butter chunks are apparent. 
%
If you have a beating machine\sidenote{Electrical mixer for dough}, just go throwing the butter there a chunk at the time with the machine on low speed.

\marginnote[2cm]{
	\begin{kaobox}[frametitle=Why butter in the end?]
		Butter has a bit of fat, which acts as a shortening to the gluten, as result, it is more difficult to knead the dough with the butter there from the beginning.
	\end{kaobox}
}

With that baby dough kneaded, leave to proof for about an hour, or until it almost double in volume\sidenote{It will become a big girl ready to giggle in the party.}.
%
Transfer the dough to a surface with a bit of flour, and fold it into a tight ball.
%
Divide the dough in $8$ portions (usually arround $110 (g)$ each), and form them into $8$ tight balls\sidenote{This girl is sticky, use a light coat of flour on your hands and part of the working surface.}
%
Put these babies in the baking tray and cover them with a tea towel, and leave them to grow until they double, or a bit more.

Egg-wash, sesame seeds, egg-wash on top before putting in the oven.

\section{Baking}

Preheat the oven to $180-200^oC$ .
% 
Buns in the centre of the oven.
%
Bake until they are delicious-golden on top.

\section{Experiments}

Making the \textit{roux}\sidenote{\href{https://www.kingarthurflour.com/blog/2018/07/23/how-to-convert-a-bread-recipe-to-tangzhong}{water roux or tangzhong}} improves the elasticity of the dough, making it easier to roast it with butter, keeping its shape while eating, and avoiding it to break apart.
%
First test with $20\%$ of the flour as \textit{roux} resulted in a very nice structure.
%
However, the shape was a bit off, which I blame on the poor shaping and baking in two layers. \rev{need to retest.}



