\setchapterstyle{kao}
\setchapterpreamble[u]{\margintoc}
\chapter{Basic Brioche / Croissant}\label{burger buns}

\section{Ingredients}

\begin{multicols}{2}
	\begin{description}
		\item[500 g] Strong Wheat Flour
		\item[125 g] Water
		\item[125 g] Milk
		\item[12 g] Fresh Yeast
		\item[50 g] Cold butter for Dough
		\item[250 g] Butter for Layers
		\item[100 g] Sugar
		\item[10 g] Salt
		\item[1] egg for wash
		\item[some] Rosemary
	\end{description}
\end{multicols}	

\section{Preparation}
Mix all the dough ingredients for the dough, except the butter. Knead until kneaded and add the dough butter by pieces.

Now, for Croissants:

While the dough is kneading, open the butter for the layers with a rolling pin between parchment paper sheets, try to make it as square as possible.

Rub the dough with flour, open it twice as large as the butter, centre the butter in the dough and close it\sidenote{Rubbing a bit of water helps to close the dough}. Then, repeat the following about $3$ times:

\begin{itemize}
	\item Open the dough; 
	\item Make a 4 layers fold;
	\item Wrap it on plastic tightly;
	\item Rest in the coldest place in the fridge for $1$ hour.
\end{itemize}

\section{Shaping}
Open the dough until it is about half finger thick, and cut the edges to have clean edges.
%
Cut triangles, the size an number of croissants depend on the size of the triangles\sidenote{You gotta do some math.}.
%
Make an incision on the bottom of the triangles so that part separates while rolling, as such the croissant wont be too thick in the middle.

Egg-wash them and leave then to grow until twice the original size.

\section{Baking}

Preheat the oven to $160^oC$.
% 
Egg-wash again before putting the babies in the centre of the oven.
%
Bake until they are delicious-golden on top.

