\setchapterstyle{kao}
\setchapterpreamble[u]{\margintoc}
\chapter{Husband Trap Shroom Pasta}

\section{Ingredients}
Quantities are an abstract concept.

\begin{multicols}{2}
	\begin{description}
		\item[per capita] Fresh not-dried pasta
		\item[2] Fat garlic teeth
		\item[some] variety of mushrooms
		\item[some] Butter
		\item[some] \gls{evo}
		\item[1 spoon] Flour
		\item[some] Thime
		\item[some] White wine
		\item[\rev{100 g}] Cream
		\item[some] prezzemolo (and cipollina)
		\item[pinches] Salt, Pepper, spices.
	\end{description}
\end{multicols}

\section{Preparation}

Slice and dice the more common mushrooms quite small. Slice the uglier, and chubbier mushrooms at about half a finger thickness. Add them to a large large pot with (melted) butter and \gls{evo}, give a good mix.
%
Fry without steering much under a medium heat\sidenote{Too hot you will burn the butter and/or the oil. We do not want the brown to come from the burnt butter, it has to come from the shrooms.}, until nice and deep brown.
%
Stir and flip the shrooms every so often, while sipping the wine.
%
Add the thinly sliced garlic af late stages of frying. \rev{Add some thime here for a deep thime taste.}

\marginnote[-7.5cm]{
	\begin{kaobox}[frametitle=Timing:]
		Start chopping the shrooms. As they fry, slice the garlic, then chop the prezzemolo.
		
		If you have help and space, someone can go opening and cutting the pasta while you fry the mushrooms.
	\end{kaobox}
}

Deglaze with a couple of splashes of white wine, you should have some liquid after the alcohol evaporates.
%
Add the flour and mix to combine the fats and liquid. Sip the wine. Cook for a couple of minutes\sidenote{Add some water at this stage to interrupt the cooking.}.

This is a good point to start boiling water for the pasta.

Add the cream\sidenote{Do not use sour cream or heavy cream.}, possibly more water, and seasoning. 
%
\rev{Also add some thime here for a freshet thime taste.}
%
Let it cook, while steering every so often, under a low heat until the cream thickens.

Add the prezzemolo chopped by a bit less than 1 finger to the sauce right after you add the pasta to the water\sidenote{I am trusting you are using fresh pasta. If you are using dried one, adjust the timings. The prezzemolo should not be there for too long, max. a couple of minutes before the cooked pasta come in.}

\section{Experiments}

I am not sure when is the best time to add the Thime.